### 2022-01-21 manuscript/methodology.tex
pequenas correcoes no texto para submissao da review 1 (submetido)

Using equations \ref{eq:k-x-oriented} and \ref{eq:l-x-oriented} the grid indices $k(i) = 2$, $l(i) = 2$ and $k(j) = 3$, $l(j) = 1$ can be calculated. Equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij} define $\Delta k_{ij} = -1$ and $\Delta l_{ij} = 1$, which represents the the value in the fifth row and third column of matrices $\Delta\mathbf{K}$ and $\Delta\mathbf{L}$ (equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}), respectively. If we use the matrix coordinates $x_{4}$ ($y_{4}$) for the observation point and $x_{2}$ ($y_{2}$) for the source, lead us to the same values for $\Delta k_{ij}$ and $\Delta l_{ij}$ (fourth row and second column of equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}).

>>>>

Using equations \ref{eq:k-x-oriented} and \ref{eq:l-x-oriented} the grid indices $k(i) = 2$, $l(i) = 2$ and $k(j) = 3$, $l(j) = 1$ can be calculated. Equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij} define $\Delta k_{ij} = -1$ and $\Delta l_{ij} = 1$, which represents the the value in the fifth row and third column of matrices $\Delta\mathbf{K}$ and $\Delta\mathbf{L}$ (equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}), respectively. Using the matrix coordinates $x_{4}$ ($y_{4}$) for the observation point and $x_{2}$ ($y_{2}$) for the source, lead us to the same values for $\Delta k_{ij}$ and $\Delta l_{ij}$ (fourth row and second column of equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}).
